---
title: "Carrizo Stuffs"
author: "Kari Norman"
date: "10/31/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Carl made a cool tool for dealing with data that can't be put up on a repo (whether because it's not shareable or because it's too big) called piggyback (https://github.com/ropensci/piggyback). The github read me gives a good explanation of how to set it up and what it does, but basically its a way to upload files as "assests" (i.e. attachements) to a repo. People can see the names of the attachments under the release of the repo but not the files themselves.

```{r}
library(piggyback)

#to add files to a repo (only have to do this once)
pb_track('data/*.csv') %>% #track all the csv files in the data folder
+     pb_upload(repo = 'karinorman/resilience_group') #upload all the files that are being tracked 

#and to get it back! (this should stick the files in your data file)
pb_download(repo = "karinorman/resilience_group")

```


```{r}
library(tidyverse)
library(here)

invert <- read_csv(paste0(here("data"), "/CarrizoInvertComp_2007-2015.csv"))
invert_id <- read_csv(paste0(here('data'), "/CarrizoInvertInfo_2007-2015.csv"))
```


